
\documentclass[aspectratio=43]{beamer}
% Theme works only with a 4:3 aspect ratio
\usetheme{CSCS}

% define footer text
\newcommand{\footlinetext}{Insert\_Footer}

% Select the image for the title page
\newcommand{\picturetitle}{cscs_images/image3.pdf}
\newcommand{\nestmc}{nestMC}
%\newcommand{\picturetitle}{cscs_images/image5.pdf}
%\newcommand{\picturetitle}{cscs_images/image6.pdf}


% Please use the predifined colors:
% cscsred, cscsgrey, cscsgreen, cscsblue, cscsbrown, cscspurple, cscsyellow, cscsblack, cscswhite

\author{Ben Cumming, CSCS}
\title{\nestmc Hackathon}
\subtitle{Kickoff}
\date{\today}

\begin{document}

% TITLE SLIDE
\cscstitle

% EMPTY SLIDE
\begin{frame}
\end{frame}

%************************************************
\begin{frame}{Agenda}
    \begin{info}{a title}
        \begin{enumerate}
            \item Schedule for the week
            \item Status update admin
            \item Status update for \nestmc
        \end{enumerate}
    \end{info}
\end{frame}

%************************************************
\begin{frame}{Schedule}
    The schedule isn't set in stone. We have 3 full days, or $3\frac{1}{2}$ if you are around on Friday afternoon.
    \begin{enumerate}
        \item   Project management ($\frac{1}{2}$ day)
        \item   Bernstein Poster and Talk (at least $1\frac{1}{2}$ days)
        \item   Hacking (proposed topic GPU implementation of \nestmc)
    \end{enumerate}
\end{frame}

%************************************************
\begin{frame}{Status: Posters}
    Posters for HBP and Bernstein...
    \begin{itemize}
        \item   both A0 portrait
        \item   both BYO (no need to send ahead of time)
        \item   I have reserved a slot at HBP Summit for our poster with SP 7
        \item   Have we received confirmation for Bernstein poster?
        \item   I have already got a \LaTeX template
        \item   Wouter and I can work on the posters
    \end{itemize}
\end{frame}

%************************************************
\begin{frame}{Status: Bernstein Talk}
    \begin{itemize}
        \item   Sam and I have done some Brainstorming
        \item   Sam, Alex and Ben can work on the talk
        \item   not much to say here\dots
        \item   we have 45 minutes? 35 presentation, 10 discussion?
    \end{itemize}
\end{frame}

%************************************************
\begin{frame}{Status: Networking}
    \begin{itemize}
        \item   Michael Hines has responded very positively to emails, and will meet at HBP Summit.
        \item   I want to organize other meetings at HBP Summit:
        \begin{itemize}
            \item   BBP CoreNeuron developers (separately to Michael). Try to be positive.
            \item   Marcel Stimberg: the sole developer of Brian 2. Might be an opportunity to provide him with a back end (because what he has at the moment is not so good.)
        \end{itemize}
        \item   We have to follow up with Ivan at Stanford.
    \end{itemize}
\end{frame}

%************************************************
\begin{frame}{Status: Networking}
    \begin{itemize}
        \item   Michael Hines has responded very positively to emails, and will meet at HBP Summit.
        \item   I want to organize other meetings at HBP Summit:
        \begin{itemize}
            \item   BBP CoreNeuron developers (separately to Michael). Try to be positive.
            \item   Marcel Stimberg: the sole developer of Brian 2. Might be an opportunity to provide him with a back end (because what he has at the moment is not so good.)
        \end{itemize}
        \item   We have to follow up with Ivan at Stanford.
    \end{itemize}
\end{frame}

%************************************************
\cscsthankyou{That's all}

\end{document}
